\documentclass[10pt]{beamer}

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usepackage{pgfplots}

\usetheme{Madrid}

\title{Remote information reachability: the Virtual SIB}
\author{Alessandra Persano, Fabio Viola}
\date{}

\begin{document}

\begin{frame}
\frametitle{Scenario}
\end{frame}

\begin{frame}
\frametitle{Software architecture}

The software architecture is composed by three pieces:

\begin{itemize}
\item {\bf Ancillary SIB}: stores informations about Virtual SIBs and
  remote SIBs to make them reachable;

\item {\bf Virtual SIB}: it has a public IP address and so it is a
  reachable SIB (not a real one, but we'll talk about it later);

\item {\bf Publisher}: it is a software agent that resides on the real
  SIB's host and interacts with the virtual SIB.
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Virtual SIB}

It is a black box. A KP can interact with the virtual SIB without
noticing that it is not a one. It's just a process that acts as a SIB but\dots

\

The main purpose of the Virtual SIB it's just routing requests from
the KPs to the real SIBs and confirms from the real SIBs to the
KPs. Not only. The Virtual SIB examinates messages to mantain
coherence and remove duplicates.

\end{frame}

\begin{frame}[fragile]
\frametitle{Publisher}

The real sib, to communicate with the virtual SIB, needs a software
agent that does the trick. This software component is the {\bf
  publisher} that act as KP to the real SIB and communicates directly
with the Virtual SIB. 

\end{frame}

\begin{frame}[fragile]
\frametitle{Publisher}

How does he inform the Virtual SIB about its presence? With a SSAP
message that we defined:

\begin{center}
\scriptsize
\begin{verbatim}
<SSAP_message>
	<node_id>a49d259b-e26d-40b4-a169-af1befe367cf-03cc02f9-dc7d-4462-974d-0a9d88b86416</node_id>
	<space_id>X</space_id>
	<transaction_type>REGISTER</transaction_type>
	<message_type>REQUEST</message_type>
	<transaction_id>?</transaction_id>
</SSAP_message>
\end{verbatim}
\end{center}

The virtual SIB replies with the following message:

\begin{center}
\scriptsize
\begin{verbatim}
<SSAP_message>
	<node_id>a49d259b-e26d-40b4-a169-af1befe367cf-03cc02f9-dc7d-4462-974d-0a9d88b86416</node_id>
	<space_id>X</space_id>
	<transaction_type>REGISTER</transaction_type>
	<message_type>CONFIRM</message_type>
	<transaction_id>?</transaction_id>
</SSAP_message>
\end{verbatim}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Join / Leave}
\end{frame}

\begin{frame}
\frametitle{Insert}
\end{frame}

\begin{frame}
\frametitle{Remove}
\end{frame}

\begin{frame}
\frametitle{Query}
\end{frame}

\begin{frame}
\frametitle{Subscription}
\end{frame}

\begin{frame}
\frametitle{Unsubscribe}
\end{frame}

\begin{frame}
\frametitle{Ancillary SIB}
\end{frame}

\end{document}
